WHOOMP! (There It Is) \\ Rapid Bayesian position reconstruction for gravitational\nobreakdashes-wave transients

### 2015-07-31 ms.tex
Cite effective Fisher matrix paper

    \item The Fisher information matrix will provide clues as to suitable forms of this likelihood function. Recent \ac{GW} parameter estimation literature has largely rejected the Fisher matrix, but this is mostly on the grounds of the abuse of the related \ac{CRLB} outside its realm of validity (i.e., at low to moderate \ac{SNR}) \cite{BayesianBounds,UseAbuseFisherMatrix,FisherMatrixAsymptoticExpansions,InadequaciesFisherMatrix}. However, we recognize that the block structure of the Fisher matrix provides important insights, and is a useful quantity for checking the validity of the aforementioned likelihood function, quite independent of the \ac{CRLB}.

>>>>

    \item The Fisher information matrix will provide clues as to suitable forms of this likelihood function. Recent \ac{GW} parameter estimation literature has largely rejected the Fisher matrix,\footnote{Though not entirely; see \cite{EffectiveFisherMatrix}.} but this is mostly on the grounds of the abuse of the related \ac{CRLB} outside its realm of validity (i.e., at low to moderate \ac{SNR}) \cite{BayesianBounds,UseAbuseFisherMatrix,FisherMatrixAsymptoticExpansions,InadequaciesFisherMatrix}. However, we recognize that the block structure of the Fisher matrix provides important insights, and is a useful quantity for checking the validity of the aforementioned likelihood function, quite independent of the \ac{CRLB}.
